Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-09 Paperfolder/Paperfolder.Rmd
Updated discu 30%

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke events were found to be delayed from happening among Japanese male daily milk consumers compared with non-consumers.

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015] with further additional and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event. A recent meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
<!-- - potential biological reasons -->

>>>>

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke mortality events were delayed from happening among Japanese male daily milk consumers compared with non-consumers.

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015], we further updated with more comprehensive and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event. A recent dose-response meta-analysis of 18 prospective cohort studies had also shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis however also found a slightly higher risk of stroke per 200 g/day whole milk intake from five cohort studies that were conducted on European or American population [@goldbohm2011dairy; @Iso1999].
<!-- - potential biological reasons -->

### 2020-07-09 Paperfolder/Paperfolder.tex
Updated discu 30%

In the JACC study cohort, our analysis showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke events were found to be delayed from happening among Japanese
male daily milk consumers compared with non-consumers.

These findings are in line with our previous report
\citep{wang_milk_2015} with further additional and more forthright
evidence about whether and how certain we could hold about daily
consumption of milk is contributing to a postponed stroke (mostly
cerebral infarction) mortality event. A recent meta-analysis of 18
prospective cohort studies had shown a similar negative association
\citep{DeGoede2016} between milk consumption and risk of stroke.

>>>>

In the JACC study cohort, our analysis showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke mortality events were delayed from happening among Japanese male
daily milk consumers compared with non-consumers.

These findings are in line with our previous report
\citep{wang_milk_2015}, we further updated with more comprehensive and
more forthright evidence about whether and how certain we could hold
about daily consumption of milk is contributing to a postponed stroke
(mostly cerebral infarction) mortality event. A recent dose-response
meta-analysis of 18 prospective cohort studies had also shown a similar
negative association \citep{DeGoede2016} between milk consumption and
risk of stroke. The same meta-analysis however also found a slightly
higher risk of stroke per 200 g/day whole milk intake from five cohort
studies that were conducted on European or American population
\citep{goldbohm2011dairy, Iso1999}.
